Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 introduction.tex

From a more principled or theoretical perspective, visual analytics goals
or objectives for emerging systems, described in previous work, closely match
the goals of our prototype. Adopting the terminology of X Y and Z, we noted
the following.

>>>>

From a more principled or theoretical perspective, certain visual analytics
goals or objectives for emerging systems, described in previous work,
closely match ours. We noted the following central themes.
